### 2017-09-06 README.Rmd
changed name to dynalysis

# dynanalysis

The goal of dynanalysis is to ...

@@

You can install dynanalysis from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Zouter/dynanalysis")
```

>>>>

# dynalysis

The goal of dynalysis is to ...

@@

You can install dynalysis from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Zouter/dynalysis")
```
